---
title: "Technical Report No Bugs"
output:
  pdf_document: default
  html_document: default
---
This data comes from a Gallup World Poll asking individuals to rank their life on a scale from 0 to 10 (worst to best life). The happiness index is the HappinessScore and is the average for each country. n = 121 countries, and p = 31 variables (including happiness index).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
Country_happy<- merge(X2017,countries_of_the_world)
Country_happy2 <- merge(Country_happy, percievedcorruptionwithUS)
happy_country <- Country_happy2 %>%
  na.omit()
library(stringr)
names(happy_country)<-str_replace_all(names(happy_country), c(" " = "." , "," = "" ))
names(happy_country)<-str_replace_all(names(happy_country), c("%" = "", "\\("="", "\\)"="", "\\."="", "\\$"="_", "/"="by"))


happy_country <- subset(happy_country, select = -c(HappinessRank, Whiskerhigh, Whiskerlow, EconomyGDPperCapita, Family, HealthLifeExpectancy, Freedom, Generosity, TrustGovernmentCorruption, DystopiaResidual))


class(happy_country$Phonesper1000)

happy_country<-happy_country%>%
  mutate(Phonesper1000=as.numeric(str_replace_all(Phonesper1000, ",", ".")))
class(happy_country$Phonesper1000)

happy_country<-happy_country%>%
  mutate(PopDensitypersqmi=as.numeric(str_replace_all(PopDensitypersqmi, ",", ".")))
class(happy_country$PopDensitypersqmi)

happy_country<-happy_country%>%
  mutate(Coastlinecoastbyarearatio=as.numeric(str_replace_all(Coastlinecoastbyarearatio, ",", ".")))
class(happy_country$Coastlinecoastbyarearatio)

happy_country<-happy_country%>%
  mutate(Netmigration=as.numeric(str_replace_all(Netmigration, ",", ".")))
class(happy_country$Netmigration)

happy_country<-happy_country%>%
  mutate(Arable=as.numeric(str_replace_all(Arable, ",", ".")))
class(happy_country$Arable)

happy_country<-happy_country%>%
  mutate(Crops=as.numeric(str_replace_all(Crops, ",", ".")))
class(happy_country$Crops)

happy_country<-happy_country%>%
  mutate(Agriculture=as.numeric(str_replace_all(Agriculture, ",", ".")))
class(happy_country$Agriculture)

happy_country<-happy_country%>%
  mutate(Industry=as.numeric(str_replace_all(Industry, ",", ".")))
class(happy_country$Industry)

happy_country<-happy_country%>%
  mutate(Service=as.numeric(str_replace_all(Service, ",", ".")))
class(happy_country$Service)
```

```{r}
happy_country_nocat <- subset(happy_country, select = -c(Region, Country, Climate))
happy_country_cor <- happy_country_nocat %>%
  cor(happy_country_nocat)
```

```{r}
mod1<- lm(HappinessScore~Birthrate, data= happy_country)
summary(mod1)
ggplot(happy_country, aes(x = Birthrate, y = HappinessScore)) +
 geom_point() +
 labs(x="Birthrate", y="Happiness Score")+
 geom_jitter() +
 stat_smooth(method = "lm")
```

```{r}
summary(happy_country)
names(happy_country)
mod2<- lm(HappinessScore~Infantmortalityper1000births+Literacy, data=happy_country)
summary(mod2)
ggplot(happy_country, aes(x=Infantmortalityper1000births+Literacy, y=HappinessScore)) +
  geom_point()+
  labs(x="Factors", y="Happiness Score") +
  geom_jitter()+
  stat_smooth(method = "lm")
```

```{r}
summary(happy_country)
names(happy_country)
mod3<- lm(HappinessScore~Climate, data=happy_country)
summary(mod3)
ggplot(happy_country, aes(x=Climate, y=HappinessScore)) +
  geom_point()+
  labs(x="Climate", y="Happiness Score") +
  geom_jitter()+
  stat_smooth(method = "lm")
```

```{r}
num_happy<- happy_country %>%
  select_if(is.numeric)
pairs(num_happy[,1:4], pch = 19)
```

```{r}
mod5<- lm(HappinessScore~GDP_percapita, data=happy_country)
summary(mod5)
ggplot(happy_country, aes(x=GDP_percapita, y=HappinessScore)) +
  geom_point()+
  labs(x="GDP Per Capita", y="Happiness Score") +
  geom_jitter()+
  stat_smooth(method = "lm")
```

Linear Models
```{r}
lm1<- lm(HappinessScore~Literacy, data= happy_country)
summary(lm1)
lmplot1<- ggplot(happy_country, aes(x = Literacy, y = HappinessScore)) + 
  geom_point() +
  labs(x="Literacy", y="Happiness Score")+
  geom_jitter() +
  stat_smooth(method = "lm")
lmplot1

lm2<- lm(HappinessScore~Birthrate, data= happy_country)
summary(lm2)
lmplot2<- ggplot(happy_country, aes(x = Birthrate, y = HappinessScore)) + 
  geom_point() +
  labs(x="Birthrate", y="Happiness Score")+
  geom_jitter() +
  stat_smooth(method = "lm")
lmplot2

lm3<- lm(HappinessScore~Deathrate, data= happy_country)
summary(lm3)
lmplot3<- ggplot(happy_country, aes(x = Deathrate, y = HappinessScore)) + 
  geom_point() +
  labs(x="Death Rate", y="Happiness Score")+
  geom_jitter() +
  stat_smooth(method = "lm")
lmplot3

lm4<- lm(HappinessScore~Climate, data= happy_country)
summary(lm4)
lmplot4<- ggplot(happy_country, aes(x = Climate, y = HappinessScore)) + 
  geom_point() +
  labs(x="Climate", y="Happiness Score")+
  geom_jitter() +
  stat_smooth(method = "lm")
lmplot4

lm5<- lm(HappinessScore~Population, data= happy_country)
summary(lm5)
lmplot5<- ggplot(happy_country, aes(x = Population, y = HappinessScore)) + 
  geom_point() +
  labs(x="Population", y="Happiness Score")+
  geom_jitter() +
  stat_smooth(method = "lm")
lmplot5
```

```{r}
mod255<- lm(HappinessScore~Phonesper1000 + GDP_percapita + Literacy + Deathrate, data=happy_country)
summary(mod255)
mod255plot<- ggplot(happy_country, aes(x=Phonesper1000+GDP_percapita+Literacy+Deathrate, y=HappinessScore))+
  geom_point()+
  labs(x="Factors", y="Happiness Score") +
  geom_jitter()+
  stat_smooth(method = "lm")
mod255plot
```

```{r}
lm6<- lm(HappinessScore~PercievedCorruptionScore, data= happy_country)
summary(lm6)
lmplot6<- ggplot(happy_country, aes(x = PercievedCorruptionScore, y = HappinessScore)) + 
  geom_point() +
  labs(x="Perceived Corruption", y="Happiness Score")+
  geom_jitter() +
  stat_smooth(method = "lm")
lmplot6

```

Ridge and Lasso

```{r model_matrix, message = FALSE, eval = FALSE}
library(tidyverse)
library(glmnet)
X <- model.matrix(HappinessScore ~ ., data = num_happy)[, -1]
X[1:2, ]
Y <- num_happy$HappinessScore
lambdas <- seq(from = 1e4, to = 1e-2, length.out = 100)
rm1 <- glmnet(x = X, y = Y, alpha = 0, 
              lambda = lambdas, standardize = TRUE)
summary(rm1)
class(rm1)
cv_rm1 <- cv.glmnet(X, Y, alpha = 0, lambda = lambdas)
plot(cv_rm1)

best_lambda <- cv_rm1$lambda.min
best_lambda
view(best_lambda)

set.seed(1)
training= sample(1:nrow(X), nrow(X)/2)
testing=(-training)
y_test =Y[testing]

ridge_mod2= glmnet(X[training,], Y[training], alpha=0, lambda = lambdas, thresh = 1e-12)
rm_pred = predict(ridge_mod2, s=best_lambda, newx = X[testing,])
MSE_ridge <- mean((rm_pred - y_test)^2)
MSE_ridge

#Lasso

Y2 <- num_happy$HappinessScore
lambdas <- seq(from = 1e4, to = 1e-2, length.out = 100)
lasso_mod <- glmnet(x=X, y=Y, alpha =1, lambda = lambdas, standardize = TRUE)
class(lasso_mod)

cv_lasso_mod <- cv.glmnet(X[training,], Y2[training], alpha = 1, lambda = lambdas)
plot(cv_lasso_mod)

best2_lambda <- cv_lasso_mod$lambda.min
best2_lambda

#Lasso MSE
set.seed(1)
training = sample(1:nrow(X), nrow(X)/2)
testing = (-training)
Y2_test = Y2[testing]

lasso_m2 = glmnet(X[training,], Y2[training], 
                  alpha = 1, lambda = lambdas, thresh = 1e-12)
lasso_prediction = predict(lasso_m2, s = best2_lambda, newx = X[testing,])
mean((lasso_prediction - Y2_test)^2)

out_2 <- glmnet(X,Y2, alpha = 1)
predict(out_2, type = "coefficients" , s = best2_lambda) [1:52]
```

#Ridge Try 2
```{r}
library(broom)
library(glmnet)

yridge <- num_happy$HappinessScore
xridge <- num_happy %>% data.matrix()
lambdasridge <- 10^seq(3, -2, by = -.1)

fit <- glmnet(xridge, yridge, alpha = 0, lambda = lambdasridge)
summary(fit)

cv_fit <- cv.glmnet(xridge, yridge, alpha = 0, lambda = lambdasridge)

plot(cv_fit)

opt_lambda <- cv_fit$lambda.min
opt_lambda

fit <- cv_fit$glmnet.fit
summary(fit)

ridgefinalmod= glmnet(xridge[training,], yridge[training], alpha=0, lambda = lambdas, thresh = 1e-12)
rm_pred = predict(ridge_mod2, s=best_lambda, newx = X[testing,])
```


#Lasso Try 2

```{r}
x_vars <- model.matrix(HappinessScore~. , num_happy)[,-1]
y_var <- num_happy$HappinessScore
lambda_seq <- 10^seq(2, -2, by = -.1)

# Splitting the data into test and train
set.seed(86)
train = sample(1:nrow(x_vars), nrow(x_vars)/2)
x_test = (-train)
y_test = y_var[test]

cv_output <- cv.glmnet(x_vars[train,], y_var[train], 
            alpha = 1, lambda = lambda_seq)

# identifying best lamda
best_lam <- cv_output$lambda.min
best_lam


lasso_best <- glmnet(x_vars[train,], y_var[train], alpha = 1, lambda = best_lam)
pred <- predict(lasso_best, s = best_lam, newx = x_vars[test,])

final <- cbind(y_var[test], pred)
final
```

```{r}
CountryPlot<- ggplot(happy_country, aes(x = Country, y = HappinessScore)) +
 geom_point() +
 labs(x="Country", y="Happiness Score")
CountryPlot
meanHappy<-mean(happy_country[["HappinessScore"]])
meanHappy
```

Random Forests

Regression Tree

```{r}
library(tree)
library(MASS)
regtree<- tree(HappinessScore ~ .-HappinessScore,data=num_happy)
plot(regtree)
text(regtree, pretty=0)

#Prune
tcv <- cv.tree(regtree, FUN = prune.tree)
tcv

plot(tcv$size, tcv$dev, type = "b", xlab = "n leaves", ylab = "error", cex=.75)

tcv$size[which.min(tcv$dev)]
tprune <- prune.tree(regtree, best = 8)
plot(tprune)
text(tprune, pretty = 0)
tree_est <- predict(tprune, newdata=num_happy)
MSE_test<- mean((tree_est - num_happy$HappinessScore)^2)
MSE_test

```

## Boost
```{r}
set.seed(1)
train <- sample(1:nrow(num_happy), nrow(num_happy) * .75)
traind <- num_happy[train, ]
testd <- num_happy[-train, ]
library(gbm)
boost1 <- gbm(HappinessScore ~ .-HappinessScore,data=traind,
                     distribution = "multinomial", n.trees = 50,
                     shrinkage = 0.1, interaction.depth = 1)
pred66 <- predict(boost1, newdata = testd, n.trees = 50, type = "response", shrinkage = 0.1, interaction.depth = 1)
MSE_test2<- mean((pred66 - testd$HappinessScore)^2)
MSE_test2
```

PCA

```{r}
pca1 <- prcomp(num_happy, center=TRUE, scale. =  TRUE)
summary(pca1)
str(pca1)
```

```{r}
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
```

```{r}
ggbiplot(pca1)

dat <- as.data.frame(pca1$x)
PCAPlot <- ggplot(dat, aes(x = PC1, y = PC2)) +
  geom_point(size = 3) +
  xlim(c(-3, 3)) +
  theme_bw(base_size = 18)
PCAPlot

```
Scree Plot
```{r echo = FALSE, fig.align="center", fig.height = 5.5, fig.width=7}
d1 <- data.frame(PC = 1:20,
                PVE = pca1$sdev^2 / sum(pca1$sdev^2))
ggplot(d1, aes(x = PC, y = PVE)) +
  geom_line() + 
  geom_point() +
  theme_bw(base_size = 18)
```


## Random Forest

```{r}
library(randomForest)
rf <- randomForest(HappinessScore ~ .-HappinessScore, data = traind, importance = TRUE)
rf
plot(rf)
testrf <- predict(rf, newdata=testd)
MSE2<- mean((testrf - testd$HappinessScore)^2)
MSE2
varImpPlot(rf)

```

